Technical Report

### 2017-11-06 fully-abstract-comp/technical-report.tex
added description of call implementation and a comment about future worlds and revoked regions (should we need them).

% Math packages
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{thmtools}
\usepackage{array}
\usepackage{cleveref}
\usepackage{stmaryrd}

@@

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{}{}$ implementation, i.e., the instructions $\scall[1]{r_1}{r_2} \dots \scall[\calllen]{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \tgete{r_{1t}}{\rstk}\\
    \tstore{\rstk}{r_{t1}}\\
    \tcca{\rstk}{-1}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{{\color{red} \dots}}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \tcca{\rstk}{1}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}
  \end{array}
\]
{\color{red} \dots} needs to be the offset to the seal we want to use.

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

>>>>

% Math packages
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{thmtools}
\usepackage{array}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{mathpartir}

@@

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{}{}$ implementation, i.e., the instructions $\scall[1]{r_1}{r_2} \dots \scall[\calllen]{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \tgete{r_{1t}}{\rstk}\\
    \tstore{\rstk}{r_{t1}}\\
    \tcca{\rstk}{-1}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{{\color{red} \dots}}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \tcca{\rstk}{1}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}
  \end{array}
\]
{\color{red} \dots} needs to be the offset to the seal we want to use.
The call code does the following:
\begin{itemize}
\item Store the end address of the stack to the stack (this ensures the stack is non-empty), and decrement the pointer according to convention.
\item Get the current address of the stack pointer and split according to it.
\item Retrieve the seal of the program.
\item cca the seal, so the seal to be used is active 
\item seal our private part of the stack capability.
\item Move the pc out of the pc register, adjust it to point to the first address of the return code, and seal it.
\item clear the temporaryu register.
\item cross jump to the two specified registers.
\item Upon return:
  \begin{itemize}
  \item get the base of the stack and check that it matches up with the global base of the stack.If not, fail.
  \item splice the returned stack pointer and the stack pointer for our private stack.
  \item adjust stack pointer to first empty address (the address with the end address is considered free)  
  \item clear the temporary registers.
  \end{itemize}
\end{itemize}

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\lau{06-11-2017: If we need to introduce revoked regions like we hade for the local capabilities, we may consider the following: For the future world relation require the existance of a bijection from region names to region names. For all regions in the present world the future region is given by the bijection. This would mean that reinstantiation would happen simply by giving a bijection that maps to the new region. In other words, the weird shadowing would not be necessary.
  \begin{mathpar}
    \inferrule{ \dom(W') \supseteq \dom(W) \\ \exists m : \RegionName \fun \RegionName, \text{ $m$ injective} \ldotp \forall r \in \dom(W) \ldotp W'(m(r)) \pubft W(r) }
    { W' \pubft W }
  \end{mathpar}
}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]
